---
title: "FA2"
author: "Dizon, Kiana Marie"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### 2. An experiment consists of tossing two fair coins. Use R to simulate this experiment 100 times and obtain the relative frequency of each possible outcome. Hence, estimate the probability of getting one head and one tail in any order.

```{r number2}
# Number of simulations
n_sim <- 100

# Simulate tossing two fair coins and store the results
results <- replicate(n_sim, sample(c("H", "T"), 2, replace = TRUE))

# Initialize counts for each outcome
count_HT <- 0
count_TH <- 0

# Count the number of times each outcome occurs
for (i in 1:n_sim) {
  if (all(results[, i] == c("H", "T"))) {
    count_HT <- count_HT + 1
  } else if (all(results[, i] == c("T", "H"))) {
    count_TH <- count_TH + 1
  }
}

# Calculate the relative frequency of each outcome
freq_HT <- count_HT / n_sim
freq_TH <- count_TH / n_sim

# Estimate the probability of getting one head and one tail in any order
p_one_head_one_tail <- freq_HT + freq_TH

#Results
freq_HT
freq_TH
p_one_head_one_tail
```
#### 3. An experiment consists of rolling a die. Use R to simulate this experiment 600 times and obtain the relative frequency of each possible outcome. Hence, estimate the probability of getting each of 1, 2, 3, 4, 5, and 6.
```{r number3}
# Number of simulations
n_sim <- 600

# Simulate rolling a fair six-sided die
results <- sample(1:6, n_sim, replace = TRUE)

# Count the number of times each outcome occurs
counts <- table(results)

# Calculate the relative frequency of each outcome
relative_frequencies <- counts / sum(counts)

# results
relative_frequencies
```